---
title: "svengala_811240683 Assignment Module 4- Solve LP Model Using R"
author: "Sai Supriya Vengala"
date: '2022-09-23'
output:
  html_document: default
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

------------------------------------------------------------------------

------------------------------------------------------------------------

```{r}
#install.packages("lpSolve")
library("lpSolve") #Activating the lpSolve Package
```

Further going down in order to solve the problem we need to define the objective function, constraints, direction and constants

Objective Function

$$\text{The Objective function is to } Max \hspace{.3cm} Z = 420 (L_1+L_2+L_3) + 360 (M_1+M_2+M_3) + 300 (S_1+S_2+S_3)$$

\$\$

\$\$

$$ \text {which can be written as } Z = 420L_1+360M_1+300S_1+420L_2+360M_2+300S_2+420L_3+360M_3+300S_3
$$

Subject to the following constraints

$$
L_1+M_1+S_1 \le 750 
$$

$$
L_2+M_2+S_2 \le 900 
$$

$$
L_3+M_3+S_3 \le 450
$$

$$
20L_1+15M_1+12S_1 \le 13000
$$

$$
20L_2+15M_2+12S_2 \le 12000
$$

$$
20L_3+15M_3+12S_3 \le 5000
$$

$$
L_1+L_2+L_3 \le 900
$$

$$
M_1+M_2+M_3 \le 1200
$$

$$
S_1+S_2+S_3 \le 750 
$$

Non Negativity Constraints

$$
 L_1,L_2,L_3,M_1,M_2,M_3,S_1,S_2,S_3 \ge 0
$$

The above constraints can be written as below

$$
L_1+M_1+S_1+0L_2+0M_2+0S_2+0L_3+0M_3+0S_3 \le 750  
$$

$$
 0L_1+0M_1+0S_1+L_2+M_2+S_2+0L_3+0M_3+0S_3 \le 900
$$

$$
 0L_1+0M_1+0S_1+0L_2+0M_2+0S_2+L_3+M_3+S_3 \le 450
$$

$$
20L_1+15M_1+12S_1+0L_2+0M_2+0S_2+0L_3+0M_3+0S_3 \le 13000
$$

$$
0L_1+0M_1+0S_1+20L_2+15M_2+12S_2+0L_3+0M_3+0S_3 \le 12000
$$

$$
0L_1+0M_1+0S_1+0L_2+0M_2+0S_2+20L_3+15M_3+12S_3 \le 5000
$$

$$
L_1+0M_1+0S_1+L_2+0M_2+0S_2+L_3+0M_3+0S_3 \le 900
$$

$$
0L_1+M_1+0S_1+0L_2+M_2+0S_2+0L_3+M_3+0S_3 \le 1200
$$

$$
0L_1+0M_1+S_1+0L_2+0M_2+S_2+0L_3+0M_3+S_3 \le 750
$$

Defining the Objective Function - f.obj

```{r}
f.obj <- c(420,360,300,420,360,300,420,360,300)
```

Defining the Constraints - f.con

```{r}

f.con <- matrix(c(1,1,1,0,0,0,0,0,0,
                  0,0,0,1,1,1,0,0,0,
                  0,0,0,0,0,0,1,1,1,
                  20,15,12,0,0,0,0,0,0,
                  0,0,0,20,15,12,0,0,0,
                  0,0,0,0,0,0,20,15,12,
                  1,0,0,1,0,0,1,0,0,
                  0,1,0,0,1,0,0,1,0,
                  0,0,1,0,0,1,0,0,1), nrow = 9, byrow=T)

```

Defining the Direction of the constraints - f.dir

```{r}
f.dir <- c('<=',

           '<=',

           '<=',

           '<=',

           '<=',

           '<=',

           '<=',

           '<=',

           '<=')
```

Defining the constants i.e. the right hand side values - f.rhs

```{r}
f.rhs <- c(750,900,450,13000,12000,5000,900,1200,750)
```

Here lp function is used to solve the problem basing the objective function i.e. to maximizing the profits

```{r}
lp('max',f.obj,f.con,f.dir,f.rhs)
```

Calling the lp function again to get the values for the variables defined above

```{r}
lp('max',f.obj,f.con,f.dir,f.rhs)$solution
```
